### 2016-09-07 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Updated Inventor files for new burner report drawings; minor edits to Sect. 2.1 in burner report

The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs) with a 298~mm (11.75~in) depth. Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board (OSB) web as shown in Fig.~\ref{fig:TJI}. Tongue and groove oriented strand board of 18.3~mm (0.72~in) thickness was screwed to the top of the TJIs.

@@

The second floor of the Two Story Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell. The walls of the second floor were wood-frame with nominal 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers. The interior walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) durarock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board. The exterior walls were protected with 11~mm (0.44~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding.

>>>>

The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs) with a 298~mm (11.75~in) depth. Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board (OSB) web as shown in Fig.~\ref{fig:TJI}. Tongue and groove OSB of 18.3~mm (0.72~in) thickness was screwed to the top of the TJIs.

@@

The second floor of the Two Story Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell. The walls of the second floor were wood-frame with nominal 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers. The interior walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) durarock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board. The exterior walls were protected with 11~mm (0.44~in) thick OSB and 8~mm (0.31~in) fiber cement lap siding.

### 2016-09-07 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Updated Inventor files for new burner report drawings; minor edits to Sect. 2.1 in burner report

The interior walls of the first floor of each structure were framed with steel studs set to 400~mm (16~in) centers and track. Two layers of 16~mm (0.63~in) Type X gypsum board lined the steel studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board. Additionally, the ceiling was composed of two layers of 13~mm (0.5~in) thick cement board.
\FloatBarrier

The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs) with a 298~mm (11.75~in) depth. Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}. Tongue and groove oriented strand board of 18.3~mm (0.72~in) thickness was screwed to the top of the TJIs.

@@

\subsubsection{Second Floor of West Structure}
The second floor of the West Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell. The second story walls were of wood-frame with 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers. Two layers of 16~mm (0.63~in) Type X gypsum board lined the wood studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board. The exterior walls were protected with 11~mm (0.44~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding.

@@

\subsubsection{Dimensions}
Dimensioned floor plans of the East and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.

@@

The ceiling height of each structure was approximately 2.4~m (8~ft). The interior dimensions of the East Structure were approximately 6.1~m (20~ft) by 11~m (36~ft), and the interior dimensions of the first and second floors of the West Structure were 5.8~m (19~ft) by 10.7~m (35.1~ft) and 6.1~m (20~ft) by 10.9~m (35.8~ft), respectively. The stairs connecting the two floors of the West Structure started 1.6~m (5.3~ft) off the interior south wall with a width of 1.2~m (4~ft) off the interior east wall and contained a 184~mm (7.25~in) rise and 191~mm (7.5~in) run. The exterior doors of both structures, the stairwell door on the second level of the West Structure, and the square roof vent in the East Structure with a 1.2~m (4~ft) side length and 320~mm (12.75~in) depth were opened and closed at certain instances during experiments to change the ventilation patterns within the structures. The exterior doors were made of steel, and the stairwell door on the second level of the West Structure was made of lauan plywood. 
% The roof vent was composed of 16~mm (0.63~in) thick Type X gypsum board (interior side) attached to

@@

Each bare-bead thermocouple array was composed of eight thermocouples. Three bi-directional probe and solid thermocouple arrays (A7, A8, and A9) were centered in each exterior doorway of the structure and contained eight probes as shown in Fig.~\ref{fig:BDP_arrays}. The fourth bi-directional probe and solid thermocouple array (A10), also presented in Fig.~\ref{fig:BDP_arrays}, was located at the opening of the roof vent and contained three probes centered between the east and west sides of the vent. The position of each probe and thermocouple pair relative to the south wall of the vent are listed in Table~\ref{table:east_channel_list}. The total heat flux gauge/radiometer pairs were set to be aimed to view the ceiling. Gas concentrations were pulled through 9.5~mm (0.38~in) diameter stainless steel tubing. The height of each individual sensor in the sensor arrays are listed in the channel list found in Table~\ref{table:east_channel_list}.

>>>>

All first floor exterior doors were made of steel. The first floor interior walls of each structure were framed with steel studs set to 400~mm (16~in) centers and track. Two layers of 16~mm (0.63~in) Type X gypsum board lined the steel studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board. The interior ceiling of each structure was covered by two layers of 13~mm (0.5~in) thick cement board.
\FloatBarrier

The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs). Each TJI had a depth of 298~mm (11.75~in) and contained laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board (OSB) web as shown in Fig.~\ref{fig:TJI}. A layer of 18.3~mm (0.72~in) thick tongue and groove OSB was attached to the top of the TJIs.

@@

\subsubsection{Second Floor of West Structure}
The second floor of the West Structure was built on the structure's first floor wood ceiling support. The two floors were connected by a stairwell. A door made of lauan plywood was located at the top of the stairwell. The walls on the second floor were of wood-frame with 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers. Two layers of 16~mm (0.63~in) Type X gypsum board lined the interior side of the wood studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board. The interior ceiling of the second story was covered by two layers of 13~mm (0.5~in) thick cement board. The exterior side of the outer walls on the second floor were protected by 11~mm (0.44~in) thick OSB and 8~mm (0.31~in) fiber cement lap siding.

@@

% \subsubsection{Dimensions}
Dimensioned floor plans of the East and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.

@@

% The ceiling height of each compartment within the structures was approximately 2.4~m (8~ft). The interior dimensions of the East Structure were approximately 6.1~m (20~ft) by 11~m (36~ft), and the interior dimensions of the first and second floors of the West Structure were 5.8~m (19~ft) by 10.7~m (35.1~ft) and 6.1~m (20~ft) by 10.9~m (35.8~ft), respectively. The stairs connecting the two floors of the West Structure started 1.6~m (5.3~ft) off the interior south wall with a width of 1.2~m (4~ft) off the interior east wall and contained a 184~mm (7.25~in) rise and 191~mm (7.5~in) run.

The exterior doors of both structures, the stairwell door in the West Structure, and the square roof vent with a depth of 320~mm (12.75~in) in the East Structure were opened and closed at certain instances during the experiments to change the ventilation patterns within the structures.

% The exterior doors were made of steel and the stairwell door on the second level of the West Structure was made of lauan plywood.
% The roof vent was composed of 16~mm (0.63~in) thick Type X gypsum board (interior side) attached to

@@

Each bare-bead thermocouple array was composed of eight thermocouples. Three bi-directional probe and solid thermocouple arrays (A7, A8, and A9) were centered in each exterior doorway of the structure and contained eight probes as shown in Fig.~\ref{fig:BDP_arrays}. The fourth bi-directional probe and solid thermocouple array (A10), also presented in Fig.~\ref{fig:BDP_arrays}, was located at the opening of the roof vent, 320~mm (12.75~in) above the compartment ceiling. The array contained three probes centered between the east and west sides of the vent. The position of each probe and thermocouple pair relative to the south wall of the vent are listed in Table~\ref{table:east_channel_list}. The total heat flux gauge/radiometer pairs were aimed to view the ceiling. Gas concentrations were pulled through 9.5~mm (0.38~in) diameter stainless steel tubing. The height of each individual sensor in the sensor arrays are listed in the channel list found in Table~\ref{table:east_channel_list}.
